---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# jspputils

The goal of jspputils is to ...

## Installation

You can install jspputils from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jspaezp/jspputils")
```

## Example

This is a basic example which shows you how to do a template data analysis

```{r example}



```

## TODOS

- Document functions
- Add warnings when imputing values and report how many
- Check for duplications in maplot
- Make generic methods out of the plotting functions to accept fits
- Make anothr package with dummy data
- Use the former package to write the unit testing
- Make functions to output oilerplate analysis for maxquant data
- make function to find the gene names of a fit and return its name or an error 
- Use the former function in the plotting scenarios
